Software Architectures for Integrating Workflow Engines in Science Gateways

### 2016-05-13 paper.tex
done section 3 for now

\paragraph{Integration complexity} Workflow import with service invocation
requires the same components as for service invocation
(\texttt{I$_1$}=3). It requires an additional \texttt{g} interaction
for workflow import (\texttt{I$_1$}=7).

\paragraph{Robustness} Since workflow conversion is not involved in
the execution (it is an offline process), metrics are as in the
service architecture (\texttt{R$_1$=1}, \texttt{R$_2$=3}).

\paragraph{Extensibility} Since adding a new type of workflow engine
aims at supporting more workflows, we consider that it only requires
to re-implement interaction \texttt{g} in this architecture  (\texttt{E$_1$=1}). Note,
however, that implementing interaction \texttt{g} can require very
substantial work depending on the complexity of the language used by
the new engine. Similarly, adding a
new engine version only requires modifying interaction \texttt{g}
(\texttt{E$_2$=1}).  Adding a new workflow is done through
interactions \texttt{a$_1$}, \texttt{a$_2$} and \texttt{g} (\texttt{E$_3$=3}). As in the
service architecture, interfacing with a new infrastructure requires
modifications in interactions \texttt{a$_1$}, \texttt{b}, \texttt{c$_1$}
and \texttt{c$_2$} (\texttt{E$_4$=4}).

\paragraph{Scalability}  Since workflow conversion is not involved in
the execution (it is an offline process), metrics are as in the
service architecture (\texttt{S$_1$=1},
\texttt{S$_2$=1}, \texttt{S$_3$=0}).

\paragraph{Specific features} Meta-workflows are available after import,
by connecting workflows in the language used in the science gateway
(\texttt{O$_1$=0}). Debugging information is accessible as in the
service invocation architecture (\texttt{O$_2$=0}).

>>>>

\paragraph{Integration complexity} Workflow import with service invocation
requires the same components as for service invocation
(\texttt{I$_1$}=3), and an additional \texttt{g} interaction (\texttt{I$_1$}=7).

\paragraph{Robustness} Since workflow conversion is not involved in
the execution (it is an offline process), the scores are the same as for the
service architecture (\texttt{R$_1$=1}, \texttt{R$_2$=3}).

\paragraph{Extensibility} Since adding a new type of workflow engine
aims at supporting more workflows, we consider that it only requires
re-implementing interaction \texttt{g} in this architecture  (\texttt{E$_1$=1}). Note,
however, that implementing interaction \texttt{g} can require
substantial work depending on the complexity of the workflow language used by
the new engine. Similarly, adding a
new engine version only requires modifying interaction \texttt{g}
(\texttt{E$_2$=1}).  Adding a new workflow is done through
interactions \texttt{a$_1$}, \texttt{a$_2$} and \texttt{g} (\texttt{E$_3$=3}). As in the
service architecture, interfacing with a new infrastructure requires
modifications in interactions \texttt{a$_1$}, \texttt{b}, \texttt{c$_1$}
and \texttt{c$_2$} (\texttt{E$_4$=4}).

\paragraph{Scalability}  Since workflow conversion is not involved in
the execution (it is an offline process), the score is the same as for the
service architecture (\texttt{S$_1$=1},
\texttt{S$_2$=1}, \texttt{S$_3$=0}).

\paragraph{Specific features} Meta-workflows are available after import,
by connecting workflows in the language used in the science gateway
(\texttt{O$_1$=0}). 
\note{sil}{i dont understand this about meta-workflows. translation does not imply composition, right? if the science gateway is allowed to implement workflow composition, then this is probably the case in other architectures as well?}
Debugging information is accessible as in the
service invocation architecture (\texttt{O$_2$=0}).
\note{sil}{see notes 3.2}
